quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-09 paper-quollr.Rmd
Updated the image in the introduction, add section on finding the best fit

Add the image generated with S-curve data

scurve_umap1 <- read_rds("data/scurve/s_curve_noise_umap.rds")

scurve_umap2 <- read_rds("data/scurve/s_curve_noise_umap2.rds")

scurve_umap3 <- read_rds("data/scurve/s_curve_noise_umap3.rds")

scurve_umap4 <- read_rds("data/scurve/s_curve_noise_umap4.rds")

scurve_umap5 <- read_rds("data/scurve/s_curve_noise_umap5.rds")

scurve_umap6 <- read_rds("data/scurve/s_curve_noise_umap6.rds")

@@

@@

```{r}
#| label: read-limb-nldr
# Read a variety of different NLDR representations of limb
# and plot them on same aspect ratio
clr_choice <- "#0077A3"
umap_limb <- read_rds("data/limb_muscles/facs_limb_muscles_umap_n-neigbors_15_min-dist_0.1.rds")

nldr6 <- tsne_limb2 |>
  ggplot(aes(x = emb1,
             y = emb2)) +
  geom_point(alpha=0.1, size=1, colour='#ff7f00') +
  interior_annotation("f")
```

>>>>

Add the image generated with the application

```{r}
#| label: read-limb-nldr
# Read a variety of different NLDR representations of limb
# and plot them on same aspect ratio
clr_choice <- "#000000"
umap_limb <- read_rds("data/limb_muscles/facs_limb_muscles_umap_n-neigbors_15_min-dist_0.1.rds")

nldr1_org <- umap_limb |>
  ggplot(aes(x = emb1,
             y = emb2)) +
  geom_point(alpha=0.1, size=1, colour=clr_choice) +
  interior_annotation("a")

nldr2_org <- tsne_limb |>
  ggplot(aes(x = emb1,
             y = emb2)) +
  geom_point(alpha=0.1, size=1, colour=clr_choice) +
  interior_annotation("b")

nldr3_org <- phate_limb |>
  ggplot(aes(x = emb1,
             y = emb2)) +
  geom_point(alpha=0.1, size=1, colour=clr_choice) +
  interior_annotation("c")

nldr4_org <- trimap_limb |>
  ggplot(aes(x = emb1,
             y = emb2)) +
  geom_point(alpha=0.1, size=1, colour=clr_choice) +
  interior_annotation("d")

nldr5_org <- pacmap_limb |>
  ggplot(aes(x = emb1,
             y = emb2)) +
  geom_point(alpha=0.1, size=1, colour=clr_choice) +
  interior_annotation("e")

nldr6 <- tsne_limb2 |>
  ggplot(aes(x = emb1,
             y = emb2)) +
  geom_point(alpha=0.1, size=1, colour='#ff7f00') +
  interior_annotation("f")

nldr6_org <- tsne_limb2 |>
  ggplot(aes(x = emb1,
             y = emb2)) +
  geom_point(alpha=0.1, size=1, colour=clr_choice) +
  interior_annotation("f")
```

```{r}
nldr1_org + nldr2_org + nldr3_org + 
  nldr4_org + nldr5_org + nldr6_org +
  plot_layout(ncol = 3)
```

@@

## Find the most appropriate fit

@@
